---
title: "RMARKDOWN"
output: github_document
---

```{r setup, include=FALSE}
# Set CRAN mirror
options(repos = c(CRAN = "https://cran.rstudio.com/"))
```

```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r project 1}
# Load necessary libraries
library(ggplot2)
library(reshape2)
library(ggcorrplot)

# Load the dataset
walmart_sales <- read.csv("Walmart_Sales.csv")

# Select only the numeric columns needed for correlation
data_numeric <- walmart_sales[, c("Weekly_Sales", "Temperature", "Fuel_Price", "CPI", "Unemployment")]

# Calculate the correlation matrix
cor_matrix <- cor(data_numeric, use = "complete.obs")  # Use "complete.obs" to handle missing values

# Plot the full correlation heatmap
ggcorrplot(cor_matrix, 
            method = "square", 
            type = "full",       # Change to "full" to display the entire matrix
            lab = TRUE, 
            lab_size = 3, 
            title = "Correlation Matrix Heatmap",
            colors = c("blue", "white", "red"),
            outline.color = "black",
            ggtheme = theme_minimal())
```

## Conclusion
1. **Weekly Sales**

-There is a weak negative correlation between Weekly_Sales and Unemployment (-0.11), CPI (-0.07) and Temperature (-0.06). These negative values suggest that as unemployment, CPI or temperature increases, weekly sales may slightly decrease, though the correlation is very weak.

-Weekly Sales show a very weak, almost negligible, positive correlation with Fuel Price(0.01)

2. **Temperature**

-Temperature has a weak positive correlation with CPI (0.18) and Fuel_Price (0.14), indicating that temperature might slightly rise with the consumer price index and fuel price.

3. **Fuel Price**

-Fuel_Price has a weak negative correlation with CPI (-0.17), meaning that as fuel prices increase, there may be a slight decrease in the CPI, though this relationship is weak.

4. **CPI**

-Moderate negative correlation with Unemployment (-0.3), which shows a slight tendency for unemployment to rise as CPI decreases, though this is still a weak relationship.

5. **Unemployment**

-Moderate negative correlation with CPI (-0.3), indicating that when unemployment is high, CPI tends to be lower, which could reflect general economic trends.**